% https://www.usccb.org/resources/newsletter-2020-05-and-06.pdf

O God, we praise you; O Lord, we acclaim you.
Eternal Father, all the earth reveres you.
All the angels, the heavens and the Pow’rs of heaven,
Cherubim and Seraphim cry out to you in endless praise:
Holy, Holy, Holy Lord God of hosts,
heaven and earth are filled with the majesty of your glory.

The glorious choir of Apostles sings to you,
the noble company of prophets praises you,
the white-robed army of martyrs glorifies you,
Holy Church throughout the earth proclaims you,
Father of boundless majesty,
with your true and only Son,
worthy of adoration, and the Holy Spirit, Paraclete.

You, O Christ, are the King of glory,
you are the Father’s everlasting Son;
when you resolved to save the human race, 
you did not spurn the Virgin’s womb;
you overcame the sting of death
and opened wide the Kingdom of Heaven
to those who put their faith in you.
You are seated at the right hand of God
in the glory of the Father.
We believe you are the Judge who is to come. 
And so we beg you, help your servants,
redeemed by your most precious blood.
Number them among your saints in eternal glory.

Save your people, Lord, and bless your inheritance.
Shepherd them and raise them to eternal life.
Day by day, we bless you
and praise your name for endless ages evermore.
Be gracious, Lord, on this day,
and keep us from all sin.
Have mercy on us, O Lord, have mercy.
May your mercy be upon us, Lord,
as we place our trust in you.
In you, O Lord, I rest my hope:
let me never be put to shame.
