\documentclass[10pt]{article}
\RequirePackage{luatex85}
\usepackage[autocompile,allowdeprecated=true]{gregoriotex}
\usepackage{hyperref}
\usepackage[margin=0.3cm,paperheight=17.3cm,paperwidth=9.8cm]{geometry}
\usepackage[letter,center,cam]{crop}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tabularx}

\makeatletter
\DeclareRobustCommand{\versicle}{\vers@resp{-0.1em}{V}}
\DeclareRobustCommand{\response}{\vers@resp{0pt}{R}}

\newcommand{\vers@resp@sym}{\raisebox{0.2ex}{\rotatebox[origin=c]{-20}{$\m@th\rceil$}}}

\newcommand{\vers@resp}[2]{%
  {\ooalign{\hidewidth\kern#1\vers@resp@sym\hidewidth\cr#2\cr}}%
}
\makeatother
\begin{document}
\setlength{\parindent}{0pt}
\grechangestaffsize{12}
%\grechangedim{spaceabovelines}{0.15cm}{fixed}
%\grechangedim{spacebeneathtext}{0.11cm}{fixed}
\grechangedim{baselineskip}{0pt}{fixed}
\grechangestyle{initial}{\fontsize{36}{36}\selectfont}
\gregorioscore{dominicanSalve}

\begin{tabularx}{\textwidth}{X X}
\textcolor{red}{\versicle.} Dignare me laudare te, Virgo sacrata \textcolor{red}{(P.T.} Alleluia\textcolor{red}{)} &
\textcolor{red}{\versicle.} Permit me to sing your praises, holy virgin \textcolor{red}{(}Alleluia\textcolor{red}{)} \\
\textcolor{red}{\response.} Da mihi virtutem contra hostes tuos \textcolor{red}{(P.T.} Alleluia\textcolor{red}{)} &
\textcolor{red}{\response.} Strengthen me against your enemies \textcolor{red}{(}Alleluia\textcolor{red}{)}
\end{tabularx}
\begin{tabularx}{\textwidth}{X X}
\textbf{Oremus.} & \textbf{Let us pray.} \\
Concede nos famulos tuos, qu\ae{}sumus, Domine Deus, perpetua mentis
et corporis salute gaudere: et gloriosa beate Mari\ae{} semper Virginis
intercessione a pr\ae{}senti liberari tristitia et \ae{}terna perfrui
l\ae{}titia: Per Christum Dominum nostrum. \textcolor{red}{\response.} Amen. &
Lord God, give to your people the joy of continual health in mind and
body.  With the prayers of the Virgin Mary to help us, guide us through
the sorrows of this life to eternal happiness in the life to come.  We
ask this through Christ our Lord. \textcolor{red}{\response.} Amen.
\end{tabularx}
\gregorioscore{olumen}
\begin{tabularx}{\textwidth}{X X}
\textcolor{red}{\versicle.} Ora pro nobis beate Pater Dominice. \textcolor{red}{(P.T.} Alleluia\textcolor{red}{)} &
\textcolor{red}{\versicle.} Holy Father Dominic, pray for us.  \textcolor{red}{(}Alleluia\textcolor{red}{)}\\
\textcolor{red}{\response.} Ut digni efficiamur promissionibus Christi. \textcolor{red}{(P.T.} Alleluia\textcolor{red}{)} &
\textcolor{red}{\response.} That we may be made worthy of the promises of Christ. \textcolor{red}{(}Alleluia\textcolor{red}{)} \\
\textbf{Oremus.} & \textbf{Let us pray.} \\
Concede, qu\ae{}sumus, omnipotens Deus: ut qui peccatorum nostorum
pondere premimur, beati Dominici confessoris tui, Patris nostri,
patrocinio sublevemur: Per Christum Dominum nostrum.  \textcolor{red}{\response.} Amen. & 
Grant, we beseech you, almighty God, that we, who are weighed down 
by the burden of our sins, might be supported by the intercession 
of blessed Dominic, your confessor and our father, though Christ our Lord.
\textcolor{red}{\response.} Amen.
\end{tabularx}

\end{document}