% This is a one-page insert intended for Dominican Compline to go with volume 2 
% of the Liturgy of the Hours (Lent and Easter)
% Must be compiled with luatex (because of graphicx for the versicle and responsory)
\documentclass[10pt]{article}
%\RequirePackage{luatex85}
%\usepackage[autocompile,allowdeprecated=true]{gregoriotex}
\usepackage{hyperref}
\usepackage[margin=0.3cm,paperheight=17.3cm,paperwidth=9.8cm]{geometry}
\usepackage[letter,center,cam]{crop}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tabularx}

\makeatletter
\DeclareRobustCommand{\versicle}{\vers@resp{-0.1em}{V}}
\DeclareRobustCommand{\response}{\vers@resp{0pt}{R}}

\newcommand{\vers@resp@sym}{\raisebox{0.2ex}{\rotatebox[origin=c]{-20}{$\m@th\rceil$}}}

\newcommand{\vers@resp}[2]{%
  {\ooalign{\hidewidth\kern#1\vers@resp@sym\hidewidth\cr#2\cr}}%
}
\makeatother
\begin{document}
\setlength{\parindent}{0pt}
\textcolor{red}{DOMINICAN COMPLINE PROPERS FOR LENT AND EASTER}


\textcolor{red}{\versicle.} God, come to my assistance. \\
\textcolor{red}{\response.} Lord, make haste to help me. \\
Glory to the father.  As it was.  Alleluia.

\textcolor{red}{All:} \\
I confess to almighty God, 
to blessed Mary ever virgin, 
to blessed Dominic our father, 
to all the saints, and to you, brethren,
that I have sinned exceedingly
by thought, word, deed, and omission, through my fault:
I beseech you to pray for me.

\textcolor{red}{Prior or Hebdomadarian:}\\
May almighty God have mercy on us
and forgive us all our sins,
may he free us from all evil,
keep us safe and strengthen us in every good work,
and bring us to eternal life.\\
\textcolor{red}{\response.} Amen.

\textcolor{red}{Psalm antiphon for the Annunciation:}\\
\textcolor{red}{Ant.} Behold a virgin shall conceive and bear a son, and shall call his name Immanuel \textcolor{red}{(}alleluia, alleluia\textcolor{red}{)}.

\textcolor{red}{RESPONSORIES}

\textcolor{red}{Saturdays, Sundays, Solemnities, Feasts, and Holy Week:} \\
\textcolor{red}{\response.} In the midst of life we are in death.  
To whom do we look for help, but to you Lord, whose anger, with good reason, 
is enkindled because of our sins?
\textcolor{red}{*} O Holy God, O holy Mighty One, O holy and merciful Savior, give us not over to bitter death! \\
\textcolor{red}{\versicle.} Do not reject us now that we are old, when our strength fails do not forsake us Lord.
\textcolor{red}{*} O Holy God \dots

\textcolor{red}{Weekdays:} \\
\textcolor{red}{\response.} In peace I will lie down
\textcolor{red}{*} and then sleep comes at once, O Lord.\\
\textcolor{red}{\versicle.} But until I find a place for the Lord, I will give no sleep to my eyes, to my eyelids give no slumber.
\textcolor{red}{*} and then sleep comes at once, O Lord.\\
Glory to the Father.  In peace\dots

\textcolor{red}{GOSPEL CANTICLE}

\textcolor{red}{Annunciation:} \\
\textcolor{red}{Ant.} Behold, I am the handmaid of the Lord; let it be to me according to your word \textcolor{red}{(}alleluia\textcolor{red}{)}.

\textcolor{red}{First Sunday of Lent until Saturday before the third Sunday of Lent:}\\
\textcolor{red}{Ant.} Watch over us, eternal Savior, that the wily tempter may not lay hold on us, for you have been made our helper for evermore.

\textcolor{red}{Third Sunday of Lent until the Easter Triduum:}\\
\textcolor{red}{Ant.} O King, resplendent in the midst of your saints, ever worthy of prise yet surpassing all words!
You, O Lord, are in the midst of us, and we are called by your holy name; leave us not, you are our God.
And on the day of judgment, O blessed King, may you deign to place us among your saints and chosen ones.

\textcolor{red}{Easter until Ascension:} \\
\textcolor{red}{Ant.} Alleluia. The Lord has risen, Alleluia, as he told you, alleluia, alleluia.

\textcolor{red}{Ascension until Pentecost:} \\
\textcolor{red}{Ant.} Alleluia.  When Christ ascended on high, alleluia, he led a host of captives, alleluia, alleluia.

\textcolor{red}{Pentecost:} \\
\textcolor{red}{Ant.} Alleluia.  The Spirit, the Counselor, alleluia, will teach you all things, alleluia, alleluia.

\textcolor{red}{Concluding Prayer (or may use the prayer of the day):}\\
Let us pray.\\
Lord, we beg you to visit this house and banish from it all the deadly power of the enemy.
May your holy angels dwell here to keep us in peace; and may your blessing be upon us always.
We as this through Christ our Lord.  \textcolor{red}{\response.} Amen.

\textcolor{red}{Blessing:}
May the all-powerful and merciful Lord grant us a restful night and a peaceful death.  \textcolor{red}{\response.} Amen.

\textcolor{red}{The Salve and O Lumen follow with their prayers. The office is concluded with:}\\
\begin{tabularx}{\textwidth}{X X}
  May the souls of the faithful departed, through the mercy of God, rest in peace. \textcolor{red}{\response.} Amen. &
  Fidelium animae, per misericordiam Dei, requiescant in pace.  \textcolor{red}{\response.} Amen.
\end{tabularx}


\end{document}